### 2017-08-14 paper/incomeShocks-jde-r1.tex
Add health and marriage table

\begin{table}[htbp]
\begin{center}
\begin{threeparttable}
\caption{The Effects of Crop Loss on Women's Health, Absence of Partner, and Marriage Dissolution}
\label{tab:health}
\begin{tabular}{@{} l D{.}{.}{2.6} D{.}{.}{2.6}  @{}}
\toprule
                                                       & \mct{Respondent} \\
													   & \mco{BMI}           &  \mco{Illness}  	       \\ \midrule
Crop loss - 1-7 months (200 TZS or above)              &      -0.014         &       0.023         \\
                                                       &     (0.016)         &     (0.047)         \\
Pregnant                                               &       0.083\sym{***}&                     \\
                                                       &     (0.013)         &                     \\
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        \\
Woman fixed effects                                    &    \mco{Yes}        &    \mco{Yes}        \\
Observations                                           &    \mco{988}        &    \mco{988}        \\
Number of women                                        &    \mco{247}        &    \mco{247}        \\ 
\addlinespace 
                                                       &\mco{Absence/migration}&\mco{Dissolution of}\\
                                                       &\mco{of partner}     &\mco{ of marriage}\\ \midrule
Crop loss - 1-7 months (200 TZS or above)              &       0.011         &      -0.001         \\
                                                       &     (0.011)         &     (0.012)         \\
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        \\
Woman fixed effects                                    &    \mco{Yes}        &    \mco{Yes}       \\
Observations                                           &    \mco{988}        &  \mco{1,293}        \\
Number of women                                        &    \mco{247}        &    \mco{578}        \\
\addlinespace 
\bottomrule
\end{tabular}
\begin{tablenotes} \footnotesize
\item \hspace*{-0.5em} \textbf{Note.}
The sample for the dissolution of marriage includes women who are dropped
from the main sample because they do not show up in all four survey rounds
or who are dropped before they are not partnered in all four survey rounds.
Robust standard errors clustered at household level in parentheses; 
* significant at 10\%; ** significant at 5\%; *** significant at 1\%.
All values of crop lost and assets are per capita and measure in 1,000 TZS.
Variables not shown: Age of mother and number of births.
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

>>>>

% Table with pregnancy and birth results
\input{../tables/main_health_marriage.tex}
